Polynomial phase estimation by phase unwrapping 2: Asymptotic normality and simulations

### 2012-10-30 paper2.tex
Added to paper 2.  Hopefully nothing else needs to be done with this.

In this paper we consider the estimator that results from unwrapping the phase in a least squares manner.  We call this the \emph{least squares unwrapping estimator} (LSU)~\cite{McKilliam2009asilomar_polyest_lattice, McKilliamFrequencyEstimationByPhaseUnwrapping2009}\cite[Chap. 8]{McKilliam2010thesis}.  It was shown in \cite{McKilliam2009asilomar_polyest_lattice, McKilliamFrequencyEstimationByPhaseUnwrapping2009} that the LSU estimator can be represented as a \emph{nearest lattice point problem}, and Monte-Carlo simulations were used to show the LSU estimator's favourable statistical performance. %Moreover, it was noticed that the LSU appears to work correctly for coefficients anywhere in the identifiable region.  A drawback of the LSU estimator is that computing a nearest lattice point is, in general, computationally difficult.  In \cite{McKilliam2009asilomar_polyest_lattice}, two standard techniques were considered, the \emph{sphere decoder} \cite{Pohst_sphere_decoder_1981}, and \emph{Babai's nearest plane algorithm} \cite{Babai1986}. The sphere decoder was observed to have excellent statistical performance but can only be computed efficiently for $N<50$ \cite{Jalden2005_sphere_decoding_complexity}.  Computing the Babai point requires only $O(N^2)$ operations, but its statistical performance is comparatively poor at low signal to noise ratio (SNR). A major point of interest is that the lattices considered are not \emph{random}, and therefore may admit fast nearest point algorithms. 
%This has been studied in~\cite[Sec.~4.2]{McKilliam2010thesis} where polynomial time algorithms where found that compute the nearest point exactly.  Unfortantely, although polynomial time, the algorithm are still computationally very slow in practice. 
% Two main questions were raised in \cite{McKilliam2009asilomar_polyest_lattice}:
% \begin{enumerate}
% \vspace{-0.1cm}
% \item What are the asymptotic statistical properties of the LSU estimator?
% \vspace{-0.18cm}
% \item Can the structure of the lattice be exploited to obtain fast (exact or approximate) nearest point algorithms and thereby a computationally efficient estimator?
% \vspace{-0.1cm}
% \end{enumerate}
% The purpose of this paper is to answer the first question. We prove that the LSU estimator is strongly consistent and asymptotically normally distributed. 
%We also apply another known approximate nearest point algorithm, called the $K$-best method \cite{Zhan2006_K_best_sphere_decoder}, that we show provides near sphere decoder performance, but can be computed in a reasonable amount of time if $N$ is less than about 300.
In this two part series of papers we derive the asymptotic statistical properties of the LSU estimator.  The first part in the series~\cite{McKilliam_pps1_2012} asserts the strong consistency of the LSU estimator under some conditions on the distribution on the noise $\{X_n\}$.  In this second part we prove, under similar conditions on $\{X_n\}$, that the LSU estimator is asymptotically normallly distributed.

@@

As in~\cite{McKilliam_pps1_2012} the least squares unwrapping (LSU) estimator of the polynomial coefficients is the minimiser
\begin{equation}\label{eq:hatmubfLSUdefn}
\widehat{\mubf} = \arg \min_{\mubf \in B} SS(\mubf)
\end{equation}
where $B = \prod_{k=0}^{m}\left[ -\frac{0.5}{k!}, \frac{0.5}{k!}  \right)$ is a subset of $\reals^{m+1}$ defined in~\cite[Sec.~3]{McKilliam_pps1_2012} called the \emph{identifiable region}, and where the objective function
\begin{equation} \label{eq:sumofsquaresfunction}
SS(\mubf) = \sum_{n=1}^{N}\fracpart{  \Theta_{n} - \sum_{k = 0}^{m}{\mu_k n^k} }^{2},
\end{equation}
where
\begin{equation}\label{eq:noise_circ_poly}
\Theta_n = \frac{\angle{Y_n}}{2\pi} = \fracpart{ \Phi_n + y(n) },
\end{equation}
is the phase (divided by $2\pi$) of the observations $Y_1,\dots,Y_N$, and
\[
\Phi_n = \frac{1}{2\pi}\angle(1 + \rho^{-1}s_n^{-1}X_n)
\] 
are random variables representing the \emph{phase noise} observed at the reciever~\cite{Tretter1985}.  We denote by $\angle{z}$ the complex argument of the complex number $z$, and by $\fracpart{x} = x - \round{x}$ the (centered) fractional part of the real number $x$, and by $\round{x}$ the nearest integer to $x$.  We have chosen to round half integers up.

As in~\cite[Sec.~4]{McKilliam_pps1_2012} the phase noise $\Phi_1,\dots,\Phi_N$ are \emph{circular} random variables with support on $[-\nicefrac{1}{2}, \nicefrac{1}{2})$~\cite{McKilliam2010thesis,McKilliam_mean_dir_est_sq_arc_length2010,Mardia_directional_statistics,Fisher1993}.  The \emph{intrinsic mean} or \emph{Fr\'{e}chet mean} of $\Phi_n$ is defined as~\cite{McKilliam_mean_dir_est_sq_arc_length2010,Bhattacharya_int_ext_means_2003,Bhattacharya_int_ext_means_2005},
\begin{equation}\label{eq:intrmeandefn}
 \mu_{\text{intr}}  = \arg \min_{\mu \in [-\nicefrac{1}{2}, \nicefrac{1}{2})} \expect \fracpart{\Phi_n - \mu}^2, 
% %&= \arg \min_{\mu \in [-\nicefrac{1}{2}, \nicefrac{1}{2})}\int_{-\nicefrac{1}{2}}^{\nicefrac{1}{2}}\fracpart{\phi - \mu}^2f(\theta) d\theta. \label{eq:minunrappedmeandef}
\end{equation}
and the \emph{intrinsic variance} is
\[
\sigma_{\text{intr}}^2 = \expect\fracpart{\Phi_n - \mu_{\text{intr}}}^2 = \min_{\mu \in [-\nicefrac{1}{2}, \nicefrac{1}{2})} \expect \fracpart{\Phi_n - \mu}^2,
\]
where $\expect$ denotes the expected value.  Observe that if $\Phi_n$ has zero intrinsic mean then it also has zero mean and the variance and the intrinsic variance of $\Phi_n$ coincide.  The next theorem describes the asymptotic distribution of the LSU estimator.  The theorem statement makes use of the function $\dealias(\cdot)$ that is defined in~\cite[Sec.~3]{McKilliam_pps1_2012}.

@@

\begin{lemma}\label{eq:convdn}
The distribution of the vector $\dbf_N$, defined in~\eqref{eq:dnandkn}, converges to the multivariate normal with zero mean and covariance matrix $\sigma^2\Cbf$.
\end{lemma}
\begin{IEEEproof}
For any constant vector $\alphabf$, let
\[
z_N = \alphabf^\prime \dbf_N = \frac{1}{\sqrt{N}} \sum_{n=1}^{N} \Phi_n \sum_{\ell=0}^{m}\alpha_\ell\left( \frac{n}{N} \right)^\ell.
\]
By Lypanov's central limit theorem $\zbf_N$ is asymptotically normally distributed with zero mean and variance
\[
\lim_{N\rightarrow\infty} \sigma^2 \frac{1}{N} \sum_{n=1}^{N}\left( \sum_{\ell=0}^{m}\alpha_\ell\left( \frac{n}{N} \right)^\ell \right)^2 = \sigma^2 \alphabf^\prime \Cbf \alphabf.
\]
By the Cramer-Wold theorem it follows that $\dbf_N$ is asymptotically normally distributed with zero mean and covariance $\sigma^2 \Cbf$. 
% Recall that the $\ell$th element of $\dbf_N$ is
% \[
% D_{\ell,N} = \frac{1}{\sqrt{N}} \sum_{n=1}^{N}(\tfrac{n}{N})^\ell \Phi_n.
% \]
% Since the $\Phi_1, \dots, \Phi_N$ are independent, each with variance $\sigma^2$, the distribution of $D_{\ell,N}$ converges to the normal with zero mean and variance
% \[
% \lim_{N\rightarrow\infty}\var D_{\ell,N} = \sigma^2 \lim_{N\rightarrow\infty} C_{2\ell,N} = \sigma^2 C_{\ell\ell}
% \]
% by Lypanov's central limit theorem and by using~\eqref{eq:ClkNHilbert}.  The covariance between $D_{\ell,N}$ and $D_{k,N}$ is
% \[
% \covar(D_{\ell,N}, D_{k,N}) = \sigma^2 C_{\ell+k,N} \rightarrow \sigma^2 C_{\ell k}
% \]
% as $N \rightarrow \infty$, again using~\eqref{eq:ClkNHilbert}.  The proof follows.
\end{IEEEproof}

@@

This section describes the results of Monte-Carlo simulations with the least squares unwrapping (LSU) estimator, Kitchen's unwrapping estimator~\cite{Kitchen_polyphase_unwrapping_1994}, and the discrete poylnomial phase transform (DPT) estimator of Peleg and Porat~\cite{Peleg_DPT_1995}.  The sample sizes considered are $N = 10, 50, 200$ and the unknown amplitude is $\rho = 1$.  The $X_1, \dots, X_N$ are pseudorandomly generated independent and identically distributed circularly symmetric complex Gaussian random variables with variance $\sigma_c^2$.  The coefficients $\tilde{\mubf} = [\tilde{\mu}_0, \dots, \tilde{\mu}_m]$ are distributed uniformly randomly in the identifiable region $B$~\cite[Sec.~3]{McKilliam_pps1_2012}.  The number of replications of each experiment is $T = 2000$ to obtain estimates $\widehat{\mubf}_1, \dots, \widehat{\mubf}_T$ and the corresponding dealiased errors $\widehat{\lambdabf}_t = \dealias(\widehat{\mubf}_T - \tilde{\mubf})$ are computed.  The sample mean square error (MSE) of the $k$th coefficient is computed according to $\tfrac{1}{T}\sum_{t=1}^T \widehat{\lambda}_{k,t}^2$ where $\widehat{\lambda}_{k,t}$ is the $k$th element of $\widehat{\lambdabf}_t$.

Figure~\ref{plot:polyest} shows the sample MSEs obtained for a polynomial phase signal of order $m=3$.  %Results are displayed results for the zeroth and third order coefficients $\widehat{\mu}_1$ and $\widehat{\mu}_3$.  The results for $\widehat{\mu}_1$ and $\widehat{\mu}_2$ lead to similar conclusions. 
The LSU estimator can be computed by finding a nearest lattice point in a particular lattice~\cite{McKilliam2010thesis,McKilliam2009asilomar_polyest_lattice}.  When $N = 10$ and $50$ the LSU estimator can be computed exactly using a general purpose algorithm for finding nearest lattice points called the sphere~decoder~\cite{Pohst_sphere_decoder_1981,Agrell2002,Viterbo_sphere_decoder_1999}.  This is displayed by the circles in the figures.  When $N=200$ the sphere decoder is computationally intractable and we instead use an approximate nearest point algorithm called the $K$-best method~\cite{Zhan2006_K_best_sphere_decoder}.  This is displayed by the dots.  For the purpose of comparison we have also plotted the results for the $K$-best method when $N = 10$ and $50$.  The asymptotic variance predicted in Theorem~\ref{thm:asymp_proof} is displayed by the dashed line.  Provided the noise variance is small enough (so that the `threshold' is avoided) the sample MSE of the LSU estimator is close to that predicted by Theorem~\ref{thm:asymp_proof}.  The Cram\`{e}r-Rao lower bound for the variance of unbiased polynomial phase estimators in Gaussian noise is also plotted using the solid line~\cite{Peleg1991_CRB_PPS_1991}.  When the noise variance is small the asymptotic variance of the LSU estimator is close to the Cram\`{e}r-Rao lower bound.

Kitchen's unwrapping estimator and the DPT estimator perform very poorly in Figure~\ref{plot:polyest}.  The reason is that both estimators do not work correctly for all parameters in the identifiable region $B$.  For this reaon Figure~\ref{plot:polyest2} plots the sample MSE's for the estimators with the true coefficients fixed to $\tilde{\mubf} = [0.1,0.2,10^{-3},10^{-5}]$.  This is within the range suitable for the DPT estimator~\cite{Peleg_DPT_1995}.  Both Kitchen's unwrapping estimator and the DPT estimator perform better in this case.  Only results for the zeroth and third order parameters $\tilde{\mu}_0$ and $\tilde{\mu}_3$ are displayed.  The results for the other parameters are similar.

>>>>

In this paper we consider the estimator that results from unwrapping the phase in a least squares manner.  We call this the \emph{least squares unwrapping estimator} (LSU)~\cite{McKilliam2009asilomar_polyest_lattice, McKilliamFrequencyEstimationByPhaseUnwrapping2009}\cite[Chap. 8]{McKilliam2010thesis}.  It was shown in \cite{McKilliam2009asilomar_polyest_lattice, McKilliamFrequencyEstimationByPhaseUnwrapping2009} that the LSU estimator can be represented as a \emph{nearest lattice point problem}, and Monte-Carlo simulations were used to show the LSU estimator's favourable statistical performance. %Moreover, it was noticed that the LSU appears to work correctly for coefficients anywhere in the identifiable region.  A drawback of the LSU estimator is that computing a nearest lattice point is, in general, computationally difficult.  In \cite{McKilliam2009asilomar_polyest_lattice}, two standard techniques were considered, the \emph{sphere decoder} \cite{Pohst_sphere_decoder_1981}, and \emph{Babai's nearest plane algorithm} \cite{Babai1986}. The sphere decoder was observed to have excellent statistical performance but can only be computed efficiently for $N<50$ \cite{Jalden2005_sphere_decoding_complexity}.  Computing the Babai point requires only $O(N^2)$ operations, but its statistical performance is comparatively poor at low signal to noise ratio (SNR). A major point of interest is that the lattices considered are not \emph{random}, and therefore may admit fast nearest point algorithms. 
%This has been studied in~\cite[Sec.~4.2]{McKilliam2010thesis} where polynomial time algorithms where found that compute the nearest point exactly.  Unfortantely, although polynomial time, the algorithm are still computationally very slow in practice. 
% Two main questions were raised in \cite{McKilliam2009asilomar_polyest_lattice}:
% \begin{enumerate}
% \vspace{-0.1cm}
% \item What are the asymptotic statistical properties of the LSU estimator?
% \vspace{-0.18cm}
% \item Can the structure of the lattice be exploited to obtain fast (exact or approximate) nearest point algorithms and thereby a computationally efficient estimator?
% \vspace{-0.1cm}
% \end{enumerate}
% The purpose of this paper is to answer the first question. We prove that the LSU estimator is strongly consistent and asymptotically normally distributed. 
%We also apply another known approximate nearest point algorithm, called the $K$-best method \cite{Zhan2006_K_best_sphere_decoder}, that we show provides near sphere decoder performance, but can be computed in a reasonable amount of time if $N$ is less than about 300.
In this two part series of papers we derive the asymptotic statistical properties of the LSU estimator.  The first part in the series~\cite{McKilliam_pps1_2012} asserts the strong consistency of the LSU estimator under some conditions on the distribution on the noise $\{X_n\}$.  In this second part we prove, under similar conditions on $\{X_n\}$, that the LSU estimator is asymptotically normally distributed.

@@

As in~\cite{McKilliam_pps1_2012} the least squares unwrapping (LSU) estimator of the polynomial coefficients is the minimiser
\begin{equation}\label{eq:hatmubfLSUdefn}
\widehat{\mubf} = \arg \min_{\mubf \in B} SS(\mubf)
\end{equation}
where $B = \prod_{k=0}^{m}\left[ -\frac{0.5}{k!}, \frac{0.5}{k!}  \right)$ is a subset of $\reals^{m+1}$ defined in~\cite[Sec.~3]{McKilliam_pps1_2012} called the \emph{identifiable region}, and where the objective function
\begin{equation} \label{eq:sumofsquaresfunction}
SS(\mubf) = \sum_{n=1}^{N}\fracpart{  \Theta_{n} - \sum_{k = 0}^{m}{\mu_k n^k} }^{2},
\end{equation}
where
\begin{equation}\label{eq:noise_circ_poly}
\Theta_n = \frac{\angle{Y_n}}{2\pi} = \fracpart{ \Phi_n + y(n) },
\end{equation}
is the phase (divided by $2\pi$) of the observations $Y_1,\dots,Y_N$, and
\[
\Phi_n = \frac{1}{2\pi}\angle(1 + \rho^{-1}s_n^{-1}X_n)
\] 
are random variables representing the \emph{phase noise} observed at the receiver~\cite{Tretter1985}.  We denote by $\angle{z}$ the complex argument of the complex number $z$, and by $\fracpart{x} = x - \round{x}$ the (centered) fractional part of the real number $x$, and by $\round{x}$ the nearest integer to $x$.  We have chosen to round half integers up.

As in~\cite[Sec.~4]{McKilliam_pps1_2012} the phase noise $\Phi_1,\dots,\Phi_N$ are \emph{circular} random variables with support on $[-\nicefrac{1}{2}, \nicefrac{1}{2})$~\cite{McKilliam2010thesis,McKilliam_mean_dir_est_sq_arc_length2010,Mardia_directional_statistics,Fisher1993}.  The \emph{intrinsic mean} or \emph{Fr\'{e}chet mean} of $\Phi_n$ is defined as~\cite{McKilliam_mean_dir_est_sq_arc_length2010,Bhattacharya_int_ext_means_2003,Bhattacharya_int_ext_means_2005},
\begin{equation}\label{eq:intrmeandefn}
 \mu_{\text{intr}}  = \arg \min_{\mu \in [-\nicefrac{1}{2}, \nicefrac{1}{2})} \expect \fracpart{\Phi_n - \mu}^2, 
% %&= \arg \min_{\mu \in [-\nicefrac{1}{2}, \nicefrac{1}{2})}\int_{-\nicefrac{1}{2}}^{\nicefrac{1}{2}}\fracpart{\phi - \mu}^2f(\theta) d\theta. \label{eq:minunrappedmeandef}
\end{equation}
and the \emph{intrinsic variance} is
\[
\sigma_{\text{intr}}^2 = \expect\fracpart{\Phi_n - \mu_{\text{intr}}}^2 = \min_{\mu \in [-\nicefrac{1}{2}, \nicefrac{1}{2})} \expect \fracpart{\Phi_n - \mu}^2,
\]
where $\expect$ denotes the expected value.  
Observe the following property of circular random variables with zero intrinsic mean.
\begin{proposition}\label{prop:zerointmeanzeromean}
Let $\Phi$ be a circular random variable with intrinsic mean $\mu_{\text{intr}} = 0$ and intrinsic variance $\sigma^2$.  Then $\Phi$ has zero mean and variance $\sigma^2$, that is, $\expect \Phi = 0$ and $\expect (\Phi - \expect \Phi)^2  = \sigma^2$.
\end{proposition}
\begin{proof}
Assume the proposition is false and that $\mu = \expect \Phi \neq 0$.  But, then 
\begin{align*}
\sigma^2 &= \expect\fracpart{\Phi -  \mu_{\text{intr}}}^2 = \expect\fracpart{\Phi}^2 \\
&= \expect \Phi^2 >  \expect (\Phi - \mu)^2 \geq  \expect \fracpart{\Phi - \mu}^2,
\end{align*}
violating the fact that $\mu_{\text{intr}} = 0$ is the minimiser of~\eqref{eq:intrmeandefn}.
\end{proof}
The next theorem describes the asymptotic distribution of the LSU estimator.  The theorem statement makes use of the function $\dealias(\cdot)$ that is defined in~\cite[Sec.~3]{McKilliam_pps1_2012}.

@@

\begin{lemma}\label{eq:convdn}
The distribution of the vector $\dbf_N$, defined in~\eqref{eq:dnandkn}, converges to the multivariate normal with zero mean and covariance matrix $\sigma^2\Cbf$.
\end{lemma}
\begin{IEEEproof}
For any constant vector $\alphabf$, let
\[
z_N = \alphabf^\prime \dbf_N = \frac{1}{\sqrt{N}} \sum_{n=1}^{N} \Phi_n \sum_{\ell=0}^{m}\alpha_\ell\left( \frac{n}{N} \right)^\ell.
\]
Observe that $\Phi_n$ has zero mean and variance $\sigma^2$ as a result of Proposition~\ref{prop:zerointmeanzeromean}.  By Lypanov's central limit theorem $\zbf_N$ is asymptotically normally distributed with zero mean and variance
\[
\lim_{N\rightarrow\infty} \sigma^2 \frac{1}{N} \sum_{n=1}^{N}\left( \sum_{\ell=0}^{m}\alpha_\ell\left( \frac{n}{N} \right)^\ell \right)^2 = \sigma^2 \alphabf^\prime \Cbf \alphabf.
\]
By the Cram\'{e}r-Wold theorem it follows that $\dbf_N$ is asymptotically normally distributed with zero mean and covariance $\sigma^2 \Cbf$. 
% Recall that the $\ell$th element of $\dbf_N$ is
% \[
% D_{\ell,N} = \frac{1}{\sqrt{N}} \sum_{n=1}^{N}(\tfrac{n}{N})^\ell \Phi_n.
% \]
% Since the $\Phi_1, \dots, \Phi_N$ are independent, each with variance $\sigma^2$, the distribution of $D_{\ell,N}$ converges to the normal with zero mean and variance
% \[
% \lim_{N\rightarrow\infty}\var D_{\ell,N} = \sigma^2 \lim_{N\rightarrow\infty} C_{2\ell,N} = \sigma^2 C_{\ell\ell}
% \]
% by Lypanov's central limit theorem and by using~\eqref{eq:ClkNHilbert}.  The covariance between $D_{\ell,N}$ and $D_{k,N}$ is
% \[
% \covar(D_{\ell,N}, D_{k,N}) = \sigma^2 C_{\ell+k,N} \rightarrow \sigma^2 C_{\ell k}
% \]
% as $N \rightarrow \infty$, again using~\eqref{eq:ClkNHilbert}.  The proof follows.
\end{IEEEproof}

@@

This section describes the results of Monte-Carlo simulations with the least squares unwrapping (LSU) estimator, Kitchen's unwrapping estimator~\cite{Kitchen_polyphase_unwrapping_1994}, and the discrete polynomial phase transform (DPT) estimator of Peleg and Porat~\cite{Peleg_DPT_1995}.  The sample sizes considered are $N = 10, 50, 200$ and the unknown amplitude is $\rho = 1$.  The $X_1, \dots, X_N$ are pseudorandomly generated independent and identically distributed circularly symmetric complex Gaussian random variables with variance $\sigma_c^2$.  The coefficients $\tilde{\mubf} = [\tilde{\mu}_0, \dots, \tilde{\mu}_m]$ are distributed uniformly randomly in the identifiable region $B$~\cite[Sec.~3]{McKilliam_pps1_2012}.  The number of replications of each experiment is $T = 2000$ to obtain estimates $\widehat{\mubf}_1, \dots, \widehat{\mubf}_T$ and the corresponding dealiased errors $\widehat{\lambdabf}_t = \dealias(\widehat{\mubf}_T - \tilde{\mubf})$ are computed.  The sample mean square error (MSE) of the $k$th coefficient is computed according to $\tfrac{1}{T}\sum_{t=1}^T \widehat{\lambda}_{k,t}^2$ where $\widehat{\lambda}_{k,t}$ is the $k$th element of $\widehat{\lambdabf}_t$.

Figure~\ref{plot:polyest} shows the sample MSEs obtained for a polynomial phase signal of order $m=3$.  %Results are displayed results for the zeroth and third order coefficients $\widehat{\mu}_1$ and $\widehat{\mu}_3$.  The results for $\widehat{\mu}_1$ and $\widehat{\mu}_2$ lead to similar conclusions. 
The LSU estimator can be computed by finding a nearest lattice point in a particular lattice~\cite{McKilliam2010thesis,McKilliam2009asilomar_polyest_lattice}.  When $N = 10$ and $50$ the LSU estimator can be computed exactly using a general purpose algorithm for finding nearest lattice points called the sphere~decoder~\cite{Pohst_sphere_decoder_1981,Agrell2002,Viterbo_sphere_decoder_1999}.  This is displayed by the circles in the figures.  When $N=200$ the sphere decoder is computationally intractable and we instead use an approximate nearest point algorithm called the $K$-best method~\cite{Zhan2006_K_best_sphere_decoder}.  This is displayed by the dots.  For the purpose of comparison we have also plotted the results for the $K$-best method when $N = 10$ and $50$.  The asymptotic variance predicted in Theorem~\ref{thm:asymp_proof} is displayed by the dashed line.  Provided the noise variance is small enough (so that the `threshold' is avoided) the sample MSE of the LSU estimator is close to that predicted by Theorem~\ref{thm:asymp_proof}.  The Cram\'{e}r-Rao lower bound for the variance of unbiased polynomial phase estimators in Gaussian noise is also plotted using the solid line~\cite{Peleg1991_CRB_PPS_1991}.  When the noise variance is small the asymptotic variance of the LSU estimator is close to the Cram\'{e}r-Rao lower bound.

Kitchen's unwrapping estimator and the DPT estimator perform very poorly in Figure~\ref{plot:polyest}.  The reason is that both estimators do not work correctly for all parameters in the identifiable region $B$.  For this reason Figure~\ref{plot:polyest2} plots the sample MSEs for the estimators with the true coefficients fixed to $\tilde{\mubf} = [0.1,0.2,10^{-3},10^{-5}]$.  This is within the range suitable for the DPT estimator~\cite{Peleg_DPT_1995}.  Both Kitchen's unwrapping estimator and the DPT estimator perform better in this case.  Only results for the zeroth and third order parameters $\tilde{\mu}_0$ and $\tilde{\mu}_3$ are displayed.  The results for the other parameters are similar.
